---
title: "Portion Size Effect for Children at High and Low Familial Risk for Obesity (Food and Brain Study)"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
header-includes:
- \usepackage{fullpage}
- \usepackage{graphicx}
- \usepackage{subcaption}
- \usepackage{float}
- \usepackage{placeins}
- \usepackage{caption}
- \usepackage{mathtools}
# - \usepackage{multirow}
- \usepackage{amssymb}
- \usepackage{amsmath}
- \usepackage{bigstrut}
- \usepackage{geometry}
# - \usepackage{pdflscape}
- \setlength{\parskip}{1em}
geometry: margin=1.3cm
---

<!-- Copywrite -->

```{r include=FALSE, echo = FALSE}
# This script report was written by Alaina Pearce in August 2022 to 
# examine the portion size effect by risk status (data from Food and Brain Study).
#
#     Copyright (C) 2022 Alaina L Pearce
#
#     This program is free software: you can redistribute it and/or modify
#     it under the terms of the GNU General Public License as published by
#     the Free Software Foundation, either version 3 of the License, or
#     (at your option) any later version.
#
#     This program is distributed in the hope that it will be useful,
#     but WITHOUT ANY WARRANTY; without even the implied warranty of
#     MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
#     GNU General Public License for more details.
#
#     You should have received a copy of the GNU General Public License
#     along with this program.  If not, see <https://www.gnu.org/licenses/>.

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE, tidy.opts = list(comment = FALSE), echo = TRUE, fig.width=6, fig.height=4, fig.path='figs/', echo=FALSE, warning=FALSE, message=FALSE, comment = NA)
```

<!-- load startup file and any extra packages -->

```{r load, echo=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(stats)
library(haven)
library(kellertools)
library(gtsummary)
theme_gtsummary_compact()

library(car)
library(emmeans)
library(reshape2)
library(lme4)
library(lmerTest)
library(ggplot2)
library(lavaan)
library(psych)
```

```{r load_scripts, echo=FALSE, results='asis'}
source('functions.R')
source('setup.R')
source('analyses.R')
source('figures.R')
source('tables.R')
```

\clearpage

# Demographics

```{r demo_tab, echo=FALSE, results='asis'}
as_kable_extra(demo_merge_tab, caption = 'Demographics', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\
## Age - t-test

```{r demo_age_ttest, echo=FALSE}
age_ttest
```

\
## BMI Percentile - t-test
```{r demo_bmi_ttest, echo=FALSE}
bmi_ttest
bmi_sd
```

\
## FMI - t-test
```{r demo_fmi_ttest, echo=FALSE}
fmi_ttest
fmi_sd
```

\

## CEBQ SR - t-test
```{r demo_sr_ttest, echo=FALSE}
cebq_sr_ttest
cebq_sr_sd
```

\
## Sex - $\chi^2$
```{r demo_sex_chi, echo=FALSE}
sex_chi
```

\
## Income - $\chi^2$
```{r demo_income_chi, echo=FALSE}
income_chi
```

\
## Mom Education - Fisher test
```{r demo_momed_fisheri, echo=FALSE}
momed_fisher
```
\FloatBarrier
\clearpage

# CEBQ - SR
```{r cebq_sr_alpha, echo=FALSE}
sr_alpha
```
\FloatBarrier
\clearpage

# Meal Liking

```{r liking_tab, echo=FALSE, results='asis'}
as_kable_extra(liking_merge_tab, caption = 'Demographics', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\FloatBarrier
## Overall
```{r liking_risk_ttest, echo=FALSE}
kable(round(liking_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for Liking", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

## Chicken Nuggets - Liking

```{r liking_chnug_risk_ttest, echo=FALSE}
kable(round(liking_chnug_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for Liking of Chicken Nuggets", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

## Mac and Cheese - Liking

```{r liking_mac_risk_ttest, echo=FALSE}
kable(round(liking_mac_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for Liking of Mac and Cheese", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

## Grapes - Liking

```{r liking_grape_risk_ttest, echo=FALSE}
kable(round(liking_grape_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for Liking of Grapes", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

## Broccoli - Liking

```{r liking_broc_risk_ttest, echo=FALSE}
kable(round(liking_broc_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for Liking of Broccoli", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
\clearpage

## Chicken Nuggets vs Mac and Cheese
```{r chnug_mac_rank_ttest, echo=FALSE}
ps1_chnug_mac_rank_ttest
ps2_chnug_mac_rank_ttest
ps3_chnug_mac_rank_ttest
ps4_chnug_mac_rank_ttest
```
\

## Chicken Nuggets vs Grapes
```{r chnug_grape_rank_ttest, echo=FALSE}
ps1_chnug_grape_rank_ttest
ps2_chnug_grape_rank_ttest
ps3_chnug_grape_rank_ttest
ps4_chnug_grape_rank_ttest
```
\

## Chicken Nuggets vs Broccoli
```{r chnug_broc_rank_ttest, echo=FALSE}
ps1_chnug_broc_rank_ttest
ps2_chnug_broc_rank_ttest
ps3_chnug_broc_rank_ttest
ps4_chnug_broc_rank_ttest
```
\

## Mac and Cheese vs Grapes
```{r mac_grape_rank_ttest, echo=FALSE}
ps1_mac_grape_rank_ttest
ps2_mac_grape_rank_ttest
ps3_mac_grape_rank_ttest
ps4_mac_grape_rank_ttest
```
\

## Mac and Cheese vs Broccoli
```{r mac_broc_rank_ttest, echo=FALSE}
ps1_mac_broc_rank_ttest
ps2_mac_broc_rank_ttest
ps3_mac_broc_rank_ttest
ps4_mac_broc_rank_ttest
```
\

## Grapes vs Broccoli
```{r grape_broc_rank_ttest, echo=FALSE}
ps1_grape_broc_rank_ttest
ps2_grape_broc_rank_ttest
ps3_grape_broc_rank_ttest
ps4_grape_broc_rank_ttest
```
\

## Chicken Nuggets - Rank

```{r rank_chnug_risk_ttest, echo=FALSE}
kable(round(rank_chnug_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for Rank Preference of Chicken Nuggets", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

## Mac and Cheese - Rank

```{r rank_mac_risk_ttest, echo=FALSE}
kable(round(rank_mac_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for Rank Preference of Mac and Cheese", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

## Grapes - Rank

```{r rank_grape_risk_ttest, echo=FALSE}
kable(round(rank_grape_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for Rank Preference of Grapes", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

## Broccoli - Rank

```{r rank_broc_risk_ttest, echo=FALSE}
kable(round(rank_broc_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for Rank Preference of Broccoli", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
\clearpage

## Frequency of Intake

\FloatBarrier

```{r pss_tab, echo=FALSE, results='asis'}
as_kable_extra(pss_merge_tab, caption = 'Child Report - Typical Portion Selection and Intake', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\FloatBarrier

\
## Broccoli - $\chi^2$
```{r pss_broc_chi, echo=FALSE}
broc_eat_chi
```

\
## Grapes - Fisher
```{r pss_grape_chi, echo=FALSE}
grapes_eat_fisher
```

\
## Mac and Cheese - Fisher
```{r pss_mac_chi, echo=FALSE}
mac_eat_fisher
```

\
## Chicken Nuggets - Fisher
```{r pss_chknug_chi, echo=FALSE}
chknug_eat_fisher
```


```{r p_pss_tab, echo=FALSE, results='asis'}
as_kable_extra(p_pss_merge_tab, caption = 'Parent Report - Typical Portion Selection and Intake', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\FloatBarrier

\
## Broccoli - $\chi^2$
```{r p_pss_broc_chi, echo=FALSE}
p_broc_eat_chi
p_broc_freq_fisher
```

\
## Grapes - Fisher
```{r p_pss_grape_chi, echo=FALSE}
p_grapes_eat_fisher
p_grapes_freq_fisher
```

\
## Mac and Cheese - Fisher
```{r p_pss_mac_chi, echo=FALSE}
p_mac_eat_fisher
p_mac_freq_fisher
```

\
## Chicken Nuggets - Fisher
```{r p_pss_chknug_chi, echo=FALSE}
p_chknug_eat_fisher
p_chknug_freq_fisher
```



\clearpage

# Portion Size Effect

Note - Portion Size was coded in ps_prop as the proportion increase in amount served: Portion Size 1 = 0, Portion Size 2 = 0.33, Portion Size 3 = 0.66, and Portion Size 4 = 0.99. This means that a 1 unit increase is equal to a 100% increase in amount served -- the difference between Portion Size 1 and Portion Size 4.

## Total Intake

\FloatBarrier

```{r intake_tab, echo=FALSE, results='asis'}
as_kable_extra(intake_merge_tab, caption = 'Intake by Portion Size', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

## Intake by Food

\FloatBarrier

```{r intake_tab_hr, echo=FALSE, results='asis'}
as_kable_extra(hr_intake_tab, caption = 'High Risk: Intake by Portion Size', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\FloatBarrier

```{r intake_tab_lr, echo=FALSE, results='asis'}
as_kable_extra(lr_intake_tab, caption = 'Low Risk: Intake by Portion Size', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "hold_position",  full_width = FALSE)
```

\FloatBarrier

## Base Model - Test Quadratic Effect

All intake models are currently controlling for: pre-meal Freddy Fullness, child BMI, average VAS liking rating for the meal foods conducted at each meal, and meal order.

### Grams

\FloatBarrier

```{r intake_ps_gmod_base, include = TRUE}
anova(grams_ps_mod, grams_psquad_mod)
```

\FloatBarrier

```{r intake_psquad_gmod, include = TRUE, echo=FALSE, results='asis'}
grams_ps_sum <- summary(grams_ps_mod)

kable(round(grams_ps_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))

```

\FloatBarrier

<!-- \*To calculate effect of portion size by 0.33 proportion increase need to first get total quadratic effect. The $\beta$ coefficient for a quadratic effect is half the change in the linear slope for a unit increase, so total change in linear slope = 2 x ps_prop2. Since a 1 unit increase = 100% increase in portion, can then multiply the total effect by 0.33. Therefore, change in linear slope for each 33% increase in amount served = (ps_prop2 x 2) x 0.33. To calculate where the slope switches from positive to negative, need to find the vertex = -ps_prop/(ps_prop2 x 2) -->

\FloatBarrier

### kcal

\FloatBarrier

```{r intake_ps_kcalmod_base, include = TRUE}
anova(kcal_ps_mod, kcal_psquad_mod)
```

\FloatBarrier

```{r intake_ps_kcalmod, include = TRUE, echo=FALSE, results='asis'}
kcal_ps_sum <- summary(kcal_ps_mod)

kable(round(kcal_ps_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
\clearpage

## Risk Status x Portion Size (linear effect)

### Grams

Adding an interaction between Risk Status and Portion Size significantly improved model fit. 
\FloatBarrier

```{r intake_ps_gmodfit_riskxps, include = TRUE}
anova(grams_ps_mod, grams_psxrisk_mod)
```

\FloatBarrier

```{r intake_ps_gmod_riskxps, include = TRUE, echo=FALSE, results='asis'}
grams_psxrisk_sum <- summary(grams_psxrisk_mod)

kable(round(grams_psxrisk_sum$coefficients, 3), "latex",  digits = 3, caption = "Regression Table: Risk x Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
```{r intake_fig_grams_psxr, echo=FALSE, include = FALSE, fig.height = 4, fig.width = 6}
psxr_g
```


\begin{figure}
  \caption{Grams Consumed: Risk Status x Portion Size}
  \includegraphics{figs/intake_fig_grams_psxr-1.pdf}
\end{figure}

\FloatBarrier

```{r intake_ps_gmod_riskxps_slopes, include = TRUE, echo=FALSE, results='asis'}
kable(test(grams_psxrisk_slopes$emtrends), "latex",  digits = 3, caption = "Estimated Simple Slopes: Risk Status x Linear Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier

```{r intake_ps_gmod_riskxps_emmeans, include = TRUE, echo=FALSE, results='asis'}
kable(grams_psxrisk_emmeans_tab, "latex",  digits = 3, caption = "Estimated Marginal Means: Risk Status x Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r intake_ps_gmod_riskxps_ttests, include = TRUE}
grams_ps1risk_ttest
grams_ps2risk_ttest
grams_ps3risk_ttest
grams_ps4risk_ttest
```

\FloatBarrier

#### No Plate Cleaners

\FloatBarrier

```{r intake_ps_gmod_riskxps_noplateclean, include = TRUE, echo=FALSE, results='asis'}
grams_psxrisk_noplateclean_sum <- summary(grams_psxrisk_mod_noplateclean)

kable(grams_psxrisk_noplateclean_sum$coefficients, "latex",  digits = 3, caption = "Regression Table: No Plate Cleaners - Risk x Portion Size for grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

### kcal

Adding an interaction between Risk Status and Portion Size (linear effect) significantly improved model fit.

```{r intake_ps_kcalmodfit_riskxps, include = TRUE}
anova(kcal_ps_mod, kcal_psxrisk_mod)
```


\FloatBarrier

```{r intake_ps_kcalmod_riskxps, include = TRUE, echo=FALSE, results='asis'}
kcal_psxrisk_sum <- summary(kcal_psxrisk_mod)

kable(kcal_psxrisk_sum$coefficients, "latex",  digits = 3, caption = "Regression Table: Risk x Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r intake_fig_kcal_psxrisk, echo=FALSE, include = FALSE, fig.height = 4, fig.width = 6}
psxr_kcal
```

\begin{figure}
  \caption{kCal Consumed: Risk Status x Portion Size}
  \includegraphics{figs/intake_fig_kcal_psxrisk-1.pdf}
\end{figure}

\FloatBarrier

```{r intake_ps_kcalmod_rxps_emtrends, include = TRUE, echo=FALSE, results='asis'}
kable(test(kcal_psxrisk_slopes$emtrends), "latex",  digits = 3, caption = "Estimated Simple Slopes: Risk Status x Linear Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier


```{r intake_ps_kcalmod_riskxps_emmeans, include = TRUE, echo=FALSE, results='asis'}
kable(kcal_psxrisk_emmeans_tab, "latex",  digits = 3, caption = "Estimated Marginal Means: Risk Status x Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier


```{r intake_ps_kcalmod_riskxps_ttests, include = TRUE}
kcal_ps1risk_ttest
kcal_ps2risk_ttest
kcal_ps3risk_ttest
kcal_ps4risk_ttest
```
\FloatBarrier

#### No Plate Cleaners

\FloatBarrier

```{r intake_ps_kcalmod_riskxps_noplateclean, include = TRUE, echo=FALSE, results='asis'}
kcal_psxrisk_mod_noplateclean_sum <- summary(kcal_psxrisk_mod_noplateclean)

kable(kcal_psxrisk_mod_noplateclean_sum$coefficients, "latex",  digits = 3, caption = "Regression Table: No Plate Cleaners - Risk x Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier
\clearpage

# Exploratory Analyses: Individual Foods 

```{r intake_fig_grams_psxrxfood, echo=FALSE, include = FALSE, fig.height = 4, fig.width = 6}
psxr_eachfood_g
```

\


```{r intake_fig_kcal_psxrxfood, echo=FALSE, include = FALSE, fig.height = 4, fig.width = 6}
psxr_eachfood_kcal
```

\


## Chicken Nuggets

### Grams

#### Base Model

The difference between models with and without quadratic effect was not significant indicating the added model parameters/complexity did not improve model fit. Should only model chicken nugget gram intake with linear effect.

\FloatBarrier

```{r chnug_ps_gmod_base, include = TRUE}
anova(grams_chnug_ps_mod, grams_chnug_ps_psquad_mod)
```

\FloatBarrier

#### Risk x Portion Size

\FloatBarrier

```{r chnug_ps_gmod_ps, include = TRUE, echo=FALSE, results='asis'}
grams_chnug_ps_sum <- summary(grams_chnug_ps_mod)

kable(grams_chnug_ps_sum$coefficients, "latex",  digits = 3, caption = "Chicken Nugget - Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r chnug_ps_gmod_riskps, include = TRUE, echo=FALSE, results='asis'}
grams_chnug_psxrisk_sum <- summary(grams_chnug_psxrisk_mod)

kable(grams_chnug_psxrisk_sum$coefficients, "latex",  digits = 3, caption = "Chicken Nugget - Risk x Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r intake_fig_g_psxr_chnug, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
psxr_chnug_g
```


\FloatBarrier
\clearpage

### kcal

#### Base Model

The difference between models with and without quadratic effect was not significant indicating the added model parameters/complexity did not improve model fit. Should only model chicken nugget kcal intake with linear effect.

\FloatBarrier

```{r chnug_ps_kcalmod_base, include = TRUE}
anova(kcal_chnug_ps_mod, kcal_chnug_ps_psquad_mod)
```

\FloatBarrier

#### Risk x Portion Size

\FloatBarrier

```{r chnug_ps_kcalmod_ps, include = TRUE, echo=FALSE, results='asis'}
kcal_chnug_ps_sum <- summary(kcal_chnug_ps_mod)

kable(kcal_chnug_ps_sum$coefficients, "latex",  digits = 3, caption = "Chicken - Nugget Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r chnug_ps_kcalmod_riskxps, include = TRUE, echo=FALSE, results='asis'}
kcal_chnug_psxrisk_sum <- summary(kcal_chnug_psxrisk_mod)

kable(kcal_chnug_psxrisk_sum$coefficients, "latex",  digits = 3, caption = "Chicken - Nugget Risk x Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r intake_fig_kcal_psxr_chnug, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
psxr_chnug_kcal
```

\FloatBarrier
\clearpage

## Mac and Cheese

### Grams

#### Base Model

The difference between models with and without quadratic effect was not significant indicating the added model parameters/complexity did not improve model fit. Should only model chicken nugget gram intake with linear effect.

\FloatBarrier

```{r mac_ps_gmod_base, include = TRUE}
anova(grams_mac_ps_mod, grams_mac_ps_psquad_mod)
```

\FloatBarrier

#### Risk x Portion Size

\FloatBarrier

```{r mac_ps_gmod_ps, include = TRUE, echo=FALSE, results='asis'}
grams_mac_ps_sum <- summary(grams_mac_ps_mod)

kable(grams_mac_ps_sum$coefficients, "latex",  digits = 3, caption = "Mac and Cheese - Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r mac_ps_gmod_riskps, include = TRUE, echo=FALSE, results='asis'}
grams_mac_psxrisk_sum <- summary(grams_mac_psxrisk_mod)

kable(grams_mac_psxrisk_sum$coefficients, "latex",  digits = 3, caption = "Mac and Cheese - Risk x Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

The interaction between Risk Status and Portion Size was not significant so it was removed from the model.

```{r mac_ps_gmod_risk_ps, include = TRUE, echo=FALSE, results='asis'}
grams_mac_ps_risk_sum <- summary(grams_mac_ps_risk_mod)

kable(grams_mac_ps_risk_sum$coefficients, "latex",  digits = 3, caption = "Mac and Cheese - Risk x Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r intake_fig_g_psxr_mac, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
psxr_mac_g
```

\FloatBarrier
\clearpage

### kcal

#### Base Model

The difference between models with and without quadratic effect was not significant indicating the added model parameters/complexity did not improve model fit. Should only model chicken nugget kcal intake with linear effect.

\FloatBarrier

```{r mac_ps_kcalmod_base, include = TRUE}
anova(kcal_mac_ps_mod, kcal_mac_ps_psquad_mod)
```

\FloatBarrier

#### Risk x Portion Size

\FloatBarrier

```{r mac_ps_kcalmod_ps, include = TRUE, echo=FALSE, results='asis'}
kcal_mac_ps_sum <- summary(kcal_mac_ps_mod)

kable(kcal_mac_ps_sum$coefficients, "latex",  digits = 3, caption = "Mac and Cheese - Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r mac_ps_kcalmod_riskxps, include = TRUE, echo=FALSE, results='asis'}
kcal_mac_psxrisk_sum <- summary(kcal_mac_psxrisk_mod)

kable(kcal_mac_psxrisk_sum$coefficients, "latex",  digits = 3, caption = "Mac and Cheese - Risk x Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

The interaction between Risk Status and Portion Size was not significant so it was removed from the model.

```{r mac_ps_kcalmod_risk_ps, include = TRUE, echo=FALSE, results='asis'}
kcal_mac_ps_risk_sum <- summary(kcal_mac_ps_risk_mod)

kable(kcal_mac_ps_risk_sum$coefficients, "latex",  digits = 3, caption = "Mac and Cheese - Risk x Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier

```{r intake_fig_kcal_psxr_mac, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
psxr_mac_kcal
```

\FloatBarrier
\clearpage

## Grapes

### Grams

#### Base Model

The difference between models with and without quadratic effect was not significant indicating the added model parameters/complexity did not improve model fit. Should only model chicken nugget gram intake with linear effect.

\FloatBarrier

```{r grape_ps_gmod_base, include = TRUE}
anova(grams_grape_ps_mod, grams_grape_ps_psquad_mod)
```

\FloatBarrier

#### Risk x Portion Size

\FloatBarrier

```{r grape_ps_gmod_ps, include = TRUE, echo=FALSE, results='asis'}
grams_grape_ps_sum <- summary(grams_grape_ps_mod)

kable(grams_grape_ps_sum$coefficients, "latex",  digits = 3, caption = "Grapes - Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r grape_ps_gmod_riskps, include = TRUE, echo=FALSE, results='asis'}
grams_grape_psxrisk_sum <- summary(grams_grape_psxrisk_mod)

kable(grams_grape_psxrisk_sum$coefficients, "latex",  digits = 3, caption = "Grapes - Risk x Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

The interaction between Risk Status and Portion Size was not significiant so it was removed from the model.

```{r grape_ps_gmod_risk_ps, include = TRUE, echo=FALSE, results='asis'}
grams_grape_ps_risk_sum <- summary(grams_grape_ps_risk_mod)

kable(grams_grape_ps_risk_sum$coefficients, "latex",  digits = 3, caption = "Grapes - Risk x Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier

```{r intake_fig_g_psxr_grape, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
psxr_grape_g
```


\FloatBarrier
\clearpage

### kcal

#### Base Model

The difference between models with and without quadratic effect was not significant indicating the added model parameters/complexity did not improve model fit. Should only model chicken nugget kcal intake with linear effect.

\FloatBarrier

```{r grape_ps_kcalmod_base, include = TRUE}
anova(kcal_grape_ps_mod, kcal_grape_ps_psquad_mod)
```

\FloatBarrier

#### Risk x Portion Size

\FloatBarrier

```{r grape_ps_kcalmod_ps, include = TRUE, echo=FALSE, results='asis'}
kcal_grape_ps_sum <- summary(kcal_grape_ps_mod)

kable(kcal_grape_ps_sum$coefficients, "latex",  digits = 3, caption = "Grapes - Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r grape_ps_kcalmod_riskxps, include = TRUE, echo=FALSE, results='asis'}
kcal_grape_psxrisk_sum <- summary(kcal_grape_psxrisk_mod)

kable(kcal_grape_psxrisk_sum$coefficients, "latex",  digits = 3, caption = "Grapes - Risk x Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

The interaction between Risk Status and Portion Size was not significant so it was removed from the model.

```{r grape_ps_kcalmod_risk_ps, include = TRUE, echo=FALSE, results='asis'}
kcal_grape_ps_risk_sum <- summary(kcal_grape_ps_risk_mod)

kable(kcal_grape_ps_risk_sum$coefficients, "latex",  digits = 3, caption = "Grapes - Risk x Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier

```{r intake_fig_kcal_psxr_grape, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
psxr_grape_kcal
```


\FloatBarrier
\clearpage

## Broccoli

### Grams

#### Base Model

The difference between models with and without quadratic effect was not significant indicating the added model parameters/complexity did not improve model fit. Should only model chicken nugget gram intake with linear effect.

\FloatBarrier

```{r broc_ps_gmod_base, include = TRUE}
anova(grams_broc_ps_mod, grams_broc_ps_psquad_mod)
```

\FloatBarrier

#### Risk x Portion Size


\FloatBarrier

```{r broc_ps_gmod_ps, include = TRUE, echo=FALSE, results='asis'}
grams_broc_ps_sum <- summary(grams_broc_ps_mod)

kable(grams_broc_ps_sum$coefficients, "latex",  digits = 3, caption = "Broccoli - Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier

```{r broc_ps_gmod_riskps, include = TRUE, echo=FALSE, results='asis'}
grams_broc_psxrisk_sum <- summary(grams_broc_psxrisk_mod)

kable(grams_broc_psxrisk_sum$coefficients, "latex",  digits = 3, caption = "brocs - Risk x Portion Size for Grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

Unlike other models, none of the control variables were associated with broccoli intake.

There was a significant interaction between Risk Status and Portion Size. 

```{r brock_ps_gmod_riskps_slopes, include = TRUE, echo=FALSE, results='asis'}
kable(test(grams_broc_psxrisk_slopes), "latex",  digits = 3, caption = "Estimated Simple Slopes: Risk Status x Portion Size for Broccoli grams", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```


\FloatBarrier

```{r intake_fig_g_psxr_broc, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
psxr_broc_g
```


\FloatBarrier
\clearpage

### kcal

#### Base Model

The difference between models with and without quadratic effect was not significant indicating the added model parameters/complexity did not improve model fit. Should only model chicken nugget kcal intake with linear effect.

\FloatBarrier

```{r broc_ps_kcalmod_base, include = TRUE}
anova(kcal_broc_ps_mod, kcal_broc_ps_psquad_mod)
```

\FloatBarrier

#### Risk x Portion Size

\FloatBarrier

```{r broc_ps_kcalmod_ps, include = TRUE, echo=FALSE, results='asis'}
kcal_broc_ps_sum <- summary(kcal_broc_ps_mod)

kable(kcal_broc_ps_sum$coefficients, "latex",  digits = 3, caption = "Broccoli - Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r broc_ps_kcalmod_riskxps, include = TRUE, echo=FALSE, results='asis'}
kcal_broc_psxrisk_sum <- summary(kcal_broc_psxrisk_mod)

kable(kcal_broc_psxrisk_sum$coefficients, "latex",  digits = 3, caption = "brocs - Risk x Portion Size for kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

Unlike other models, none of the control variables were associated with broccoli intake.

There was a significant interaction between Risk Status and Portion Size. 

```{r broc_ps_kcalmod_riskps_slopes, include = TRUE, echo=FALSE, results='asis'}
kable(test(kcal_broc_psxrisk_slopes), "latex",  digits = 3, caption = "Estimated Simple Slopes: Risk Status x Portion Size for Broccoli kcal", booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"))
```

\FloatBarrier

```{r intake_fig_kcal_psxr_broc, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 6}
psxr_broc_kcal
```

\FloatBarrier
\clearpage

# Exploratory Analyses: Mediated Moderation

Since broccoli was the only food showing a Risk Status x Portion Size interaction, I tested whether broccoli intake mediates the overall Risk x Potion Size interaction using a mediated moderation model.

## Grams

\FloatBarrier

```{r broc_medmod_grams_riskxps, include = TRUE}
summary(med_mod_psgrams_fit)
```

\FloatBarrier

There was a significant level indirect effect (p = 0.036) indicating that broccoli intake mediated the interaction between risk status and portion size for gram intake.



## kcal

\FloatBarrier

```{r broc_medmod_kcal_riskxps, include = TRUE}
summary(med_mod_pskcal_fit)
```

\FloatBarrier

There was a significant level indirect effect (p = 0.048) indicating that broccoli intake mediated the interaction between risk status and portion size for kcal intake.
